%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                 %
%                     SECTION                     %
%                                                 %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Apparatus}
\label{sec:sec005}

For the material and apparatus, it is essential to capture the session apprehending the user interactions. In our case, we will record this interaction by using the \hyperlink{}{Some Tool 00.0 (000.0.0)} to obtain all interactions. We will pair this video tool with a user watch tool called \hyperlink{}{Other Tool Link}. All instruments will help us to capture where and when are users interacting. By looking at the test participant's reactions, we find a lot of information regarding the prototype design.

\hfill

The material used in the test sessions for the user interface consists of:

\begin{itemize}
\item Item 1: it will allow the user to interact with the some aspects;
\item Item 2: it will allow the user to interact with the some aspects;
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                 %
%                     SECTION                     %
%                                                 %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Technical Details}

To produce this traditional environment, and since we can simulate with a laptop, the mouse and keyboard interaction, we are using a Mobile Mouse 0000 together with the \hyperlink{}{Computer Link} (Model, 00-inch, Early 0000) with a standard integrated keyboard on the laptop.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                 %
%                     SECTION                     %
%                                                 %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Devices}

Traditional interaction remains the most common way to interact with user interfaces in an environment. Unfortunately, most of this interaction is made by low profile equipment that makes users produce more errors and take more time interacting with those User Interfaces (UI).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                 %
%                     SECTION                     %
%                                                 %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{User Interactions}

The systems have several buttons that allows the user to interact or access to a set of user interface features. Each item of the following list represents each metaphoric icon.

The buttons are as follows:

\hfill

\begin{itemize}
\item Button 1
\item Button 2
\item Button 3
\item Button 4
\item Button 5
\end{itemize}

\hfill

\subsection{Software}

To track our user interactions across our system, we are using \hyperlink{}{Some Tool Link}. This tool is an analytic package allowing us to follow our users remotely. It also provides two critical pieces of functionality, among others, that can aid in remote user testing.